Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2020-02-06 Tex/Old text/chapters/chapter02.tex
thesis update

In this Thesis, CPAchecker will be configurated as bounded model checker.

@@

In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, stand-alone systems can be split into several categories, as described below. Since the goal of this Thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.

>>>>

In this thesis, CPAchecker will be configured as a bounded model checker.

@@

In the specific case of isolated communities, depending on the type of load, cost, resources availability, and the load requirements, stand-alone systems can be split into several categories, as described below. Since the goal of this thesis is to present solutions only to isolated/ off-grid applications, on-grid or hybrid configurations are not discussed here.

### 2020-02-06 Tex/Old text/chapters/chapteroptimization.tex
thesis update

In this Chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking. Diagrams, flowcharts, and algorithm give support and explain the solutions.

@@

It is important to emphasize that the complete explanation of the theoretical basis of the subject discussed here is presented in the Chapter~\nameref{chap:background}. In addition, knowledge of the literature is essential to aid understanding.

@@

In this Chapter we showed in detail how the state-of-the-art computer science method of automated synthesis has been adapted to use in stand-alone solar PV systems in order to obtain optimal project sizing. Moreover, it was possible to illustrate how the proposed method compares with the traditional use of a simulation tool for the same purpose.

Detailed diagrams, flowcharts and algorithms with pseudo-code were presented as support for the proposed work and to aid understanding. Also listed, were the assumptions underlying the automated verification and simulation software.

>>>>

In this chapter, we detail methodology used for optimal sizing of stand-alone solar PV systems, more specifically using model checking. Diagrams, flowcharts, and algorithm give support and explain the solutions.

@@

It is important to emphasize that the complete explanation of the theoretical basis of the subject discussed here is presented in the chapter~\nameref{chap:background}. In addition, knowledge of the literature is essential to aid understanding.

@@

In this chapter we showed in detail how the state-of-the-art computer science method of automated synthesis has been adapted to use in stand-alone solar PV systems in order to obtain optimal project sizing. Moreover, it was possible to illustrate how the proposed method compares with the traditional use of a simulation tool for the same purpose.

Detailed diagrams, flowcharts and algorithm with pseudo-code were presented as support for the proposed work and to aid understanding. Also listed, were the assumptions underlying the automated verification and simulation software.

### 2020-02-06 Tex/Old text/chapters/chapterverification.tex
thesis update

In this Chapter, we detail the methodology adopted to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking. Diagrams, flowcharts, and algorithms support and explain the solutions. The experimentation, case studies, and results are also presented. In addition, the Chapter contains a comparison with a specialized simulation tool, and also the use of different verifiers that evaluate performance by means of automated verification. Tables, commented reports, and graphic outputs are presented to aid  understanding.

Additionally, we present all assumptions and premises adopted, all of which support the results/conclusions, with direct impact on them. Usually, a premise is an unquestionable fact, however assumptions can be questioned. Unlike premises, assumptions are not explicit and need to be deciphered. With that in mind, we perform a detailed explanation of all assumptions over the course of the Chapter.

It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in Chapter 2, ~\nameref{chap:background}. In addition, knowledge of the literature is essential to aid understanding.

@@

This Chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, it also identified six threats to the validity of the results that bear further assessment.

@@

This Chapter showed in details how the state-of-the-art computer science method of automated verification was adapted to be used in stand-alone solar PV systems in order to validate their behavior. Moreover, it was possible to illustrate the comparative differences in how the proposed method and the traditional method of simulation work.

@@

Furthermore, in this Chapter verifiers with the proposed automated verification using model checking were compared, which demonstrated that 'incremental' ESBMC had the best overall performance. CBMC was not conclusive, presented out of memory issues in all cases. CPAchecker had similar quality results than ESBMC, but with a slower performance for all cases.

>>>>

In this chapter, we detail the methodology adopted to perform formal verification of stand-alone solar PV systems using formal methods, more specifically model checking. Diagrams, flowcharts, and algorithms support and explain the solutions. The experimentation, case studies, and results are also presented. In addition, the chapter contains a comparison with a specialized simulation tool, and also the use of different verifiers that evaluate performance by means of automated verification. Tables, commented reports, and graphic outputs are presented to aid  understanding.

Additionally, we present all assumptions and premises adopted, all of which support the results/conclusions, with direct impact on them. Usually, a premise is an unquestionable fact, however assumptions can be questioned. Unlike premises, assumptions are not explicit and need to be deciphered. With that in mind, we perform a detailed explanation of all assumptions over the course of the chapter.

It is important to emphasize that the theoretical basis of the subject presented in this chapter was discussed in chapter 2, ~\nameref{chap:background}. In addition, knowledge of the literature is essential to aid understanding.

@@

This chapter presented a favorable assessment of the proposed method. % over a diverse set of real-world benchmarks. 
Nevertheless, it also identified six threats to the validity of the results that bear further assessment.

@@

This chapter showed in details how the state-of-the-art computer science method of automated verification was adapted to be used in stand-alone solar PV systems in order to validate their behavior. Moreover, it was possible to illustrate the comparative differences in how the proposed method and the traditional method of simulation work.

@@

Furthermore, in this chapter verifiers with the proposed automated verification using model checking were compared, which demonstrated that 'incremental' ESBMC had the best overall performance. CBMC was not conclusive, presented out of memory issues in all cases. CPAchecker had similar quality results than ESBMC, but with a slower performance for all cases.

### 2020-02-06 Tex/Old text/chapters/introduction.tex
thesis update

Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems to tackle two issues: validation of a designed system and optimal sizing. Validation when a sized system must be evaluated in order to decide if it meets the design requirements and user needs. \textcolor{red}{this sentence is confusing... Optimization, when there exist just the requirements and the PV system, is not sized, or when the user tries to obtain a better solution that he or she has}. We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in comparison with specialized simulation tools, supported by real data from installed PV systems.

@@

\textcolor{red}{The following two paragraphs are too long! Please consider breaking them into smaller sentences!}

Concerning the proposed \textbf{automated verification} technique, this thesis makes three main contributions: \textbf{first}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; \textbf{second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; \textbf{third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.

In the area of \textbf{automated synthesis}, our study makes a further three original contributions: \textbf{first}, it is the first application of a sound and automated formal synthesis approach which can provide accurate results for optimal sizing of stand-alone PV systems; \textbf{second}, we propose a variant CEGIS method of synthesis with striking differences of how the Synthesize and Verify phases from the original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and \textbf{third}, experimental results in seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tools: our solution is far more detailed and closer to real PV systems than solutions presented by simulation.

>>>>

Our approach deals with the theoretical and pragmatic aspects of using model checking in stand-alone solar PV systems to tackle two issues: validation of a designed system and optimal sizing.

Validation is a important issue when a sized system must be evaluated in order to decide if it meets the design requirements and user needs. In other words, it is a way to guarantee that a sized PV system will not fail (stopping to supply energy to a house, for example) after deployment at the field.

\textcolor{red}{Optimization is important when there exist (just) the requirements of the house to be electrified. In our particular case, we need a optimal PV system solution, in technical and economical terms, that can show us a list of equipment to be bought and how it will be connected together (configuration)}.

We thus develop algorithms and the corresponding tools; we then evaluate them through several case studies, in comparison with specialized simulation tools, supported by real data from installed PV systems.

@@

\textcolor{red}{My comment: paragraphs broken in small and organized parts:}

Concerning the proposed \textbf{automated verification} technique, this thesis makes three main contributions: 
\begin{itemize}
\item \textbf{First}, we propose an algorithm written in the C programming language which implements the automated verification method to formally check the sizing and the operation of a given stand-alone PV system; 
\item \textbf{Second}, we evaluate the verification technique by comparing three state-of-the-art model checkers in five real case studies; and 
\item \textbf{Third}, experimental results show that this approach can find subtle design errors in stand-alone PV systems not easily detected by other approaches based on simulation.
\end{itemize}

In the area of \textbf{automated synthesis}, our study makes a further three original contributions: 
\begin{itemize}
\item \textbf{First}, it is the first application of a sound and automated formal synthesis approach which can provide accurate results for optimal sizing of stand-alone PV systems; 
\item \textbf{Second}, we propose a variant CEGIS method of synthesis with striking differences of how the Synthesize and Verify phases from the original CEGIS work (without solution candidate vector and using an incremental and iterative loop to reach the optimal cost solution); and 
\item \textbf{Third}, experimental results in seven case studies show that our approach qualitatively outperforms state-of-the-art simulation tools: our solution is far more detailed and closer to real PV systems than solutions presented by simulation.
\end{itemize}
